Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-09 Response to reviewers.tex

~\\
\noindent (2) \emph{For RF, how many trees are set? }

\begin{verbatim}
As far as the number of trees is concerned, in the experiments 
section, when describing the parameter settings, 
it has been mentioned that the best performance was obtained with a 
number of trees equal to 50.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph)

~\\
\noindent (3) \emph{As we known, tree-based methods (e.g., M5P and RF) themselves embed feature selection procedure. That is, some features are chosen to build trees. It is not fair enough to compare five methods in Table 3. }

\begin{verbatim}
Although we agree with the reviewer's comment, and the RF and M5P 
have an embedded feature selection mechanism, we believe that it 
is unfair to compare them with the filter based feature selection 
methods we have deployed in our research. 
The aim is simply to show to the decision maker what are the possible 
results when we apply one of the off-the-shelf classifiers available 
in a common open source framework such as WEKA. 
Moreover, it is not uncommon in the literature to see such comparison 
between classifiers, as in the paper:
  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
  Do we need hundreds of classifiers to solve real world 
  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
which incorporates a general comparison between all these classifiers.
\end{verbatim}
%Every response should end with changes made in the paper, even if it
%is only clarification. It is not an invitation to discussion. 
% Antonio - TODO: say how this has been addressed in the paper (where it is clarified). Say if this reference has been included as new.
% JJ - Antonio, TODO by whom? If it's an issue, put it in the repo and assign it or do it yourself.
~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

@@

~\\
\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts.}

\begin{verbatim}
We have rewritten the introduction and included new paragraphs to better 
explain the problem and the aim of the paper. We have also remarked the
 contribution with the paragraphs:

"Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his control. 
That is why, using data obtained from a company that sells software for 
publishers, we analyse them and compute predictive models that can be 
mainly used as decision-aid tools for book publishers. With these models,
 publishers will be able to combine their expert knowledge about the market 
with the created forecasting models in order to get a reliable estimation of
 book sales, and, based on it, act consequently in order to maximize the 
books sold for a particular print run. This will improve the current 
decision flow that the publishers follow, which consist in analysing (in a
 subjective way) the quality of the book and its features (author, genre, 
etc), and take a `fuzzy' decision roughly between printing 300 copies 
(standard book) or 5000 (best seller).

Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales. To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books. Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark."

@@

\noindent (1) \emph{In section introduction, this manuscript should describe the contribution of this work. }

\begin{verbatim}

The reviewer is right. The main contribution of this paper to the 
state of the art was not properly described. Thus, as stated above 
in the second response to Reviewer #2, we have clarified this in 
the introduction adding new sentences and the paragraph:

"Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales. To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books. Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark."

@@

\begin{verbatim}
Reviewer is right, so we have improved Section 5, including the 
parameter settings of M5P, kNN and RF methods (see paragraph XX at 
page YY), along with the configuration parameters for the rest of 
methods.

The authors want to express our gratitude to this reviewer 
for his/her suggestions.
\end{verbatim}
% Antonio - CONCERN: don't we also put the configuration of the rest of the methods? And say it. :D 
% Could we use a table for showing them easily?
% [pedro] TODO: design the table taken the parameters/values shown in section 5.1
% Antonio - TODO: say paragraph/page where they are.

% Antonio - TODO: Say if there are new references and include them in a final section in this letter.
% yes, there are some, but is Hossam who knows what references have been added in this revision.
%------------------------------------------------------------------------------------
\section{New references added after revision}

\begin{verbatim}
[53] G.B. Huang, Q.Y. Zhu, C.K. Siew, Extreme learning machine: 
theory and applications, Neurocomputing 70 (1) (2006) 489-501.

[54] G. Huang, G.B. Huang, S. Song, K. You, Trends in extreme 
learning machines: a review, Neural Networks 61 (2015) 32-48.

[60] Wikipedia, List of Dewey decimal classes, [Online; accessed 
05-May-2016]. https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes

[71] M. A. Hall, Correlation-based feature selection for discrete 
and numeric class machine learning, in: Proceedings of the 
Seventeenth International Conference on Machine Learning, ICML2000, 
Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 2000, 
pp. 359-366.
\end{verbatim}

### 2016-09-09 paper.tex
Improving contribution and Methodology section
A big CONCERN is there. :(

Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales. To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books. Moreover, the use of a real dataset of book sales is another point to remark with respect to other works.

@@

Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}. These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
This task may also help to identify leading indicators to be considered 
by a human expert to make predictions.

In this stage, both numerical and visualisation-based approaches have been 
applied, in order to select the best variables for the forecasting methods.  
The methods to apply are those described in Section \ref{subsec:select_method},  which include rule- and tree-based algorithms, together with numerical regression methods.

The obtained models for the whole dataset have been evaluated by means of the metrics described in Section \ref{subsec:models_evaluation}. The results are presented in Section \ref{sec:experiments}. Then, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}).
Specific interpretable models have been created as a final result of the work (Section \ref{subsec:decision_trees}).

% Antonio - CONCERN - The following section seems to be bad placed now. The Methodology Section is now a bit strange with just this subsection. We should think on moving this section and reorganize/improve the methodology description.

@@

At this stage, a Feature Selection (FS) process has been carried out, 
since it is an effective dimensionality reduction technique and an essential 
preprocessing method to discard less relevant or non-useful features 
\cite{Krishnapuram2004,Chen2011_FS_PTS}.

>>>>

Our main contribution is, thus, the development of the methodology to process book sales data in order to, first find out relevant variables, and then, use these variables to process the data to accurately estimate future sales. To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books. Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark.

@@

Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.

FS methods check the relevance of all the variables of the patterns, aiming to reduce the set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
This task may also help to identify leading indicators to be considered 
by a human expert to make predictions.
At this stage of the methodology, both numerical and visualisation-based approaches have been applied, in order to select the best set of variables for the forecasting methods.

After this process has been conducted, different prediction methods have been applied on the dataset. These methods have been described in Section \ref{subsec:select_method}, and include rule- and tree-based algorithms, together with numerical regression methods.

As a result, several prediction models are obtained. Then the obtained models for the whole dataset have been evaluated by means of the metrics described in Section \ref{subsec:models_evaluation}. The results are presented in Section \ref{sec:experiments}.

After this, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}). Specific interpretable models have been created as a final result of the work (Section \ref{subsec:decision_trees}).

% Antonio - CONCERN - The following section seems to be misplaced after moving the rest to Section 2. Thus, the Methodology Section is now a bit strange with just this subsection. We should think on moving this section and reorganize/improve the methodology description.

@@
